### 2021-05-14 docs/manuscript/manuscript.tex
Rename main file as manuscript.tex

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Proportion of relevant subgraphs in the set of GRNs.}

>>>>

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Proportion of relevant subgraphs in the set of GRNs.}
The 19 subgraphs presented in this table are those presented in \nameref{S4_Fig}.
Most of the topologies presented at least one negative feedback loop (70.73\%),
and 62.46\% of them presented the I3-FFL network motif. The robustness of each
subgraph was calculated as the mean robustness of the topologies presenting that
subgraph.
